

\documentclass[10pt]{cooperCV2}
%\RequirePackage[T1]{fontenc}
\usepackage{fontspec}
\usepackage[utf8]{inputenc}
% \usepackage{fontawesome}


\begin{document}
\thispagestyle{plain}




%------------------------------------------------------------------------------
%	HEADER
%------------------------------------------------------------------------------

 
\hspace*{-\marginparsep minus \marginparwidth}%
 \begin{minipage}[t]{\textwidth+\marginparwidth+\marginparsep}%

% Socials upper top corner
%\hfill \href{mailto:kwcooper@uci.edu}{\faEnvelope \hspace{0.05cm} kwcooper@uci.edu} \\
%\null \hfill \href{http://www.kwcooper.com/}{\faHome \hspace{0.05cm} www.kwcooper.com}\\
%\null \hfill \href{https://orcid.org/0000-0002-0358-9645}{\orcid \hspace{0.05cm} 0002-0358-9645}\\
%\null \hfill \href{http://www.kwcooper.com/}{\faTwitter \hspace{0.05cm} @kw\_cooper}\\
%\null \hfill \href{http://www.kwcooper.com/}{\faGithub \hspace{0.05cm} kwcooper}\\
% Name


{\textbf{\huge{ Keiland W. Cooper }} \hfill} \\ 
[-0.15\baselineskip]%
\rule{\columnwidth}{1pt}%
\end{minipage}

\vspace{1\baselineskip}


%\section{Contact Information}
% MACROS: \rcollength is the width of the right column of the table
%             (adjust it to your liking; default is 1.85in).
%         \spacewidth is width of area between left and right boxes.
%
\newlength{\rcollength}\setlength{\rcollength}{1.45in}%
\newlength{\spacewidth}\setlength{\spacewidth}{20pt}
\begin{tabular}[t]{@{}p{\textwidth-\rcollength-\spacewidth}@{}p{\spacewidth}@{}p{\rcollength}}%

% Address box
\parbox{\textwidth-\rcollength-\spacewidth}{%
National Science Foundation Fellow\\
\href{https://neurobiology.uci.edu/}{ Department of Neurobiology and Behavior }\\
\href{http://www.uci.edu/}{ University of California, Irvine }\\

\textit{\textcolor{grey}{Last updated \today}}}

&
\parbox[m][4\baselineskip]{\spacewidth}{} &

% Non-snail-mail contact information
\parbox{\rcollength}{%
\null \href{mailto:kwcooper@uci.edu}{\farEnvelope \hspace{0.05cm} kwcooper@uci.edu} \\
\null \href{https://kwcooper.com}{\fasHome \hspace{0.05cm} kwcooper.com}\\
\null \href{https://orcid.org/0000-0002-0358-9645}{\aiOrcid \hspace{0.05cm} 0002-0358-9645}\\
\null \href{https://twitter.com/kw\_cooper}{\fabTwitter \hspace{0.05cm} @kw\_cooper}\\
%\null \href{http://www.kwcooper.com/}{\faGithub \hspace{0.05cm} kwcooper}\\
}
\end{tabular}





%------------------------------------------------------------------------------
%	
%------------------------------------------------------------------------------





%------------------------------------------------------------------------------
%	EDUCATION
%------------------------------------------------------------------------------

\section{Education} 

  

\href{http://www.iu.edu/}{\textbf{University of California, Irvine}} \\
 Ph.D., Neurobiology and Behavior \hfill \textit{In progress}



 \textit{Advisors: Dr. Norbert Fortin}\\ 

  

\href{http://www.iu.edu/}{\textbf{Quantic School of Business and Technology, D.C.}} \\
 Master of Business Administration (MBA) \hfill \textit{March 16, 2022}



 \null \hfil 

  

\href{http://www.iu.edu/}{\textbf{Indiana University, Bloomington}} \\
 B.S., Cognitive Science \textit{with Honors} \hfill \textit{May the Fourth, 2019}

 Computer science specialization \\ 
 Certificate in Neuroscience; Minor in Psychology\\  
 \textit{Advisors: Dr. Ehren Newman, Dr. Mike Jones}\\ 








%------------------------------------------------------------------------------
%	
%------------------------------------------------------------------------------





%------------------------------------------------------------------------------
%   RESEARCH TIMELINE 
%------------------------------------------------------------------------------

\section{Research Experience}
\needspace{4em}
% \myRule{\columnwidth}{1pt}
\bigskip

\begin{longtable}{lll}
% \color{gray}

 
\mytl{2019-now}{with Dr. Norbert Fortin | \textcolor{gray}{Neuroscience}  \\- \textit{Non-spatial theta sequences and precession}  \\- \textit{11 brain region electrophysiology} }
 
\mytl{2020-now}{with the GCCR | \textcolor{gray}{Neuroscience}  \\- \textit{COVID-19 and the chemical senses} }
 
\mytl{2018-now}{with ContinualAI | \textcolor{gray}{Artificial Intelligence}  \\- \textit{Building tools to aid AI research} }
 
\mytl{2019-2020}{with Dr. Bruce McNaughton | \textcolor{gray}{Neuroscience}  \\- \textit{Hippocampal and cortical replay during sleep} }
 
\mytl{2016-2019}{with Dr. Ehren Newman | \textcolor{gray}{Neuroscience / Cognitive Science}  \\- \textit{Computational modeling of ACh \& neural oscilations}  \\- \textit{Entorhinal region electrophysiology \& signal processing}  \\- \textit{Ca\textsuperscript{2+} miniscope imaging \& rodent behavior} }
 
\mytl{2018-2019}{with Dr. Mike Jones | \textcolor{gray}{Cognitive Science}  \\- \textit{Catastrophic Forgetting in connectionist language models} }
 
\mytl{2017-2018}{with Dr. Amit Hagar | \textcolor{gray}{Philosophy + Physics}  \\- \textit{The natural computation of the brain} }
 
\mytl{2015-2016}{with Dr. Susane Ressl | \textcolor{gray}{Microbiology}  \\- \textit{Structural biochemistry of synaptic proteins} }

% \bigskip

\end{longtable}





%------------------------------------------------------------------------------
%	
%------------------------------------------------------------------------------





%------------------------------------------------------------------------------
%	AWARDS
%------------------------------------------------------------------------------

\section{Awards}
\begin{longtable}{ l l @{\extracolsep{\fill}}  l @{}}
	 
	Graduate Research Fellowship (GRFP) & \textit{\textcolor{gray}{National Science Foundation}}  & \textcolor{grey}{2021} \\
	 
	DTEI Pedagogical Fellowship & \textit{\textcolor{gray}{UC Irvine}}  & \textcolor{grey}{2020} \\
	 
	Norman Weinberger Award & \textit{\textcolor{gray}{UC Irvine CNLM}}  & \textcolor{grey}{2021} \\
	 
	Graduate Travel Award & \textit{\textcolor{gray}{UC Irvine}}  & \textcolor{grey}{2021} \\
	 
	School of Biological Sciences Travel Award & \textit{\textcolor{gray}{UC Irvine BioSci}}  & \textcolor{grey}{2021} \\
	 
	Best International AI Research Organization & \textit{\textcolor{gray}{Wealth \& Finance}}  & \textcolor{grey}{2020} \\
	 
	Cognitive Science Outstanding Research & \textit{\textcolor{gray}{Indiana University}}  & \textcolor{grey}{2019} \\
	 
	GRFP (Honorable Mention) & \textit{\textcolor{gray}{National Science Foundation}}  & \textcolor{grey}{2018} \\
	 
	Outstanding Contribution in Cognitive Science & \textit{\textcolor{gray}{Indiana University}}  & \textcolor{grey}{2018} \\
	
\end{longtable}





%------------------------------------------------------------------------------
%	
%------------------------------------------------------------------------------





%------------------------------------------------------------------------------
%	PUBLICATIONS  
%------------------------------------------------------------------------------
% Add the rule here so that we can use varrying subsections 

\needspace{\headerpush}
% \myRule{\columnwidth}{1pt}\\
\section{Publications}
\textcolor{grey}{**stars** = mentee; \textbf{bold} = me}\\

 
 
	

\subsection{Preprints} 
% \textcolor{grey}{**stars** = mentee; \textbf{bold} = me}\\
\begin{etaremune}[itemindent=-1.5\bibhang, topsep=0pt,
				   itemsep=\bibsep,partopsep=0pt,parsep=0pt,leftmargin={\bibhang+\widthof{[999]}}] 
    
    \item Increasing incidence of parosmia and phantosmia in patients recovering from COVID-19 smell loss. \\
     Ohla, K., Veldhuizen, M.G., Green, T., Hannum, M.E., Bakke, A.J., Moein, S., Tognetti, A., Postma, E.M., Pellegrino, R., ... \textbf{Cooper, K. W.}, ... Hwang, L.D. and Albayay, J.. \\ (2021) medRxiv 
     
	

\end{etaremune}

 

	

\subsection{Peer Reviewed} 
% 
\begin{etaremune}[resume,itemindent=-1.5\bibhang, topsep=0pt,
				   itemsep=\bibsep,partopsep=0pt,parsep=0pt,leftmargin={\bibhang+\widthof{[999]}}] 
    
    \item Hippocampal ensembles represent sequential relationships among discrete nonspatial events \\
     Shahbaba, B., Li, L., Agostinelli, F., Saraf, M., \textbf{Cooper, K. W.}, Elias, G. A., Haghverdian, D., Baldi, P.,  Fortin, N. J.. \\ (2022) Nature Communications 13(1), 1-17
     
	
    \item Avalanche: an End-to-End Library for Continual Learning \\
     Lomonaco, V., Pellegrini, L., Cossu, A., Carta, A., Graffieti, G., Hayes, T.L., ... \textbf{Cooper K. W.}, ... Bacciu D., Maltoni D.. \\ (2021) Proceedings of the IEEE/CVF Conference on Computer Vision and Pattern Recognition 3600-3610
     
     	\begin{list}{$\drsh$}{}
     	
	      \item \textcolor{grey}{\textit{Won CLVision WB Best Library Award} }
     	
     	\end{list} 
     
	
    \item Recent smell loss is the best predictor of COVID-19 among individuals with recent respiratory symptoms. \\
     Gerkin, R. C., Ohla, K., Veldhuizen, M. G., Joseph, P. V., Kelly, C. E., Bakke, A. J., ... \textbf{Cooper, K.W.} ... and Baguma, M. . \\ (2020) Chemical senses 46
     
	
    \item Smell and taste changes are early indicators of the COVID-19 pandemic and political decision effectiveness. \\
     Pierron, D., Pereda-Loth, V., Mantel, M., Moranges, M., Bignon, E., Alva, O.,  \textbf{Cooper, K. W.}, ... Dinnella, C. . \\ (2020) Nature Communications 11(1), 1-8.
     
     	\begin{list}{$\drsh$}{}
     	
	      \item \textcolor{grey}{\textit{\#4 of Top 100 Nature Communications papers of 2020} }
     	
     	\end{list} 
     
	
    \item COVID-19 and the chemical senses: supporting players take center stage. \\
     \textbf{Cooper, K. W.}, Brann, D.H., Farruggia, M.C., Bhutani, S., Pellegrino, R., Tsukahara, T., Weinreb, C., Joseph, P.V., Larson, E.D., Parma, V. and Albers, M.W.,. \\ (2020) Neuron 107(2), 219-233
     
     	\begin{list}{$\drsh$}{}
     	
	      \item \textcolor{grey}{\textit{Top 10 Neuron papers of 2020} }
     	
     	\end{list} 
     
	
    \item More than smell—COVID-19 is associated with severe impairment of smell, taste, and chemesthesis. \\
     Parma, V., Ohla, K., Veldhuizen, M. G., Niv, M. Y., Kelly, C. E., Bakke, A. J., \textbf{Cooper. K. W.,} ..., Hayes, J. E.. \\ (2020) Chemical Senses 45(7), 609-622
     
	
    \item Coronaviruses and the chemical senses: past, present, and future \\
     Pellegrino, R., \textbf{Cooper, K. W.}, Di Pizio, A., Joseph, P. V., Bhutani, S., and Parma, V. . \\ (2020) Chemical senses 45(6), 415-422
     
	
    \item Medial entorhinal cortex activates in a traveling wave in the rat \\
     Hernandez-Perez, J. J., \textbf{Cooper, K. W.}, Newman, E. L.. \\ (2020) eLife 9
     
	
    \item Can the Machine Understand: An Evidence Based Approach to the Chinese Room \\
     \textbf{Cooper, K. W.}. \\ (2018) IU Journal of Undergraduate Research 4(1), 82-85
     
	

\end{etaremune}

 

	

\subsection{Thesis} 
% 
\begin{etaremune}[resume,itemindent=-1.5\bibhang, topsep=0pt,
				   itemsep=\bibsep,partopsep=0pt,parsep=0pt,leftmargin={\bibhang+\widthof{[999]}}] 
    
    \item Cholinergic modulation may explain hippocampal encoding and retrieval mode switching \\
     \textbf{Cooper, K. W.}. \\ (2019) Indiana University, Bloomington Undergraduate Thesis  
     
	

\end{etaremune}



\vspace{0.5cm}
\textcolor{grey}{
\textit{Total citations (as of last update):} \\
\textbf{\aiGoogleScholar} \hspace{0.05cm} Google Scholar: \textbf{743} | \textbf{\aiSemanticScholar} \hspace{0.05cm} Semantic Scholar: \textbf{699}\\
% \aiPublons \hspace{0.05cm} Publons: XX\\
}





%------------------------------------------------------------------------------
%	
%------------------------------------------------------------------------------





%------------------------------------------------------------------------------
%	ABSTRACTS
%------------------------------------------------------------------------------

\section{Selected Abstracts\\+ Talks}
\textcolor{grey}{**stars** = mentee; \textbf{bold} = me}\\

 
\begin{etaremune}[itemindent=-1.5\bibhang, topsep=0pt,
				   itemsep=\bibsep,partopsep=0pt,parsep=0pt,leftmargin={\bibhang+\widthof{[999]}}] 
    
    \item Stitching memories into predictable patterns\\ \textbf{Cooper KW}. (2022) Neuroblitz. 
     
	
    \item Hippocampal ensembles represent the sequential order of nonspatial events.\\ \textbf{Cooper KW}, Li L, Saraf MP, Elias GA, Baldi P, Shahbaba B, Fortin NJ. (2021) Plexon Data Blitz. 
     
	
    \item Hippocampal ensembles represent the sequential order of nonspatial events.\\ \textbf{Cooper KW}, Li L, Saraf MP, Elias GA, Baldi P, Shahbaba B, Fortin NJ. (2021) Program No P858.03. Chicago, IL: Society for Neuroscience. 
     
	
    \item Medial prefrontal cortex represents ordinal position within a sequence of events.\\ Elias GA, Tran AH, Saraf MP, \textbf{Cooper KW}, Shahbaba B, Fortin NJ. (2021) Program No P858.01. Chicago, IL: Society for Neuroscience. 
     
	
    \item The sequential organization of hippocampal ensemble activity provides a key temporal signal supporting the memory for the order of events.\\ Saraf MP, Haghverdian D, \textbf{Cooper KW}, Elias GA, Shahbaba B, Fortin NJ. (2021) Program No P858.02. Chicago, IL: Society for Neuroscience. 
     
	
    \item Grant writing workshop (Panelist)\\ \textbf{Cooper KW}. (2021) University of California, Irvine. 
     
	
    \item Deep neural network models learn distinguishable features from hippocampal local field potential and ensemble data\\ ***Pan, C. J., \textbf{Cooper, K. W.}, Li, L., Agostinelli, F., Saraf, M., Elias, G. A., Baldi, P.,  Shahbaba, B., Fortin, N. J.. (2021) UROP Symposium. 
     
	
    \item Avalanche: an End-to-End Library for Continual Learning\\ \textbf{Cooper K. W.}, Lomonaco, V., Pellegrini, L., Carta, A., Cossu, A., Graffieti, G.. (2021) ContinualAI Meetup. 
     
	
    \item Hippocampal theta oscillations support nonspatial sequence coding in hippocampal neurons\\ \textbf{Cooper, K. W.}, Shahbaba, B., Li, L., Agostinelli, F., Saraf, M., Elias, G. A., Bornstein, A., Baldi, P.,  Fortin, N. J.. (2021) SFN Global Connectome. 
     
	
    \item The neuroscience and AI feedback loop: Catastrophic Forgetting and Sequences\\ \textbf{Cooper, K. W.}. (2020) UCI AGS Symposium. 
     
	
    \item The Art of Email\\ \textbf{Cooper K. W.}. (2020) UCI GPS-STEM. 
     
	
    \item Dual processes of hippocampal mode switching\\ \textbf{Cooper, K. W.}. (2020) Neuromatch online Conference. 
     
	
    \item Continual Learning: neuroscience + AI.\\ \textbf{Cooper, K. W.}. (2020) Contiual AI Meetup. 
     
	
    \item Cholinergic abolition disrupts encoding and retrieval mode switching\\ \textbf{Cooper, K. W.}. (2020) 11th Annual Emerging Scientists Symposium. 
     
	
    \item The neuroscience amd AI feedback loop\\ \textbf{Cooper, K. W.}. (2019) UCI Brain. 
     
	
    \item On neuroscience and AI\\ \textbf{Cooper, K. W.}. (2019) IUJUR Research Slam. 
     
	
    \item Is theta a traveling wave in the medial entorhinal cortex?\\ Hernández J, \textbf{Cooper, K. W.}, Newman E.L.. (2018) Program No. 330.10. Society for Neuroscience. 
     
	
    \item Consequences of Catastrophic Forgetting on Semantic Representations Learned by Deep Neural Embedding Models\\ \textbf{Cooper, K. W}, Dachapally P.R, Jones M.N. (2018) Midwest CogSci. 
     
     	\begin{list}{$\drsh$}{}
     	
	     \item  \textcolor{grey}{\textit{Best poster award} }
     	
     	\end{list}
     
	
    \item Is theta in the Medial Entorhinal Cortex a Traveling Wave?\\ \textbf{Cooper, K. W.}, Hernández, J., Newman, E.L.. (2018) Society for Neuroscience, Greater Indiana Chapter. 
     
	
    \item 3D Brain Model Extraction and Virtual Applications\\ \textbf{Cooper, K. W.}. (2018) (Panelist) Media School Graduate Association Conference. 
     
	
    \item FlapAI: Genetically Evolved Neural Networks\\ \textbf{Cooper, K. W.}. (2018) Midwest Undergraduate Cognitive Science Conference. 
     
	
    \item Bridging the Gap: Natural Computation and Neural Systems\\ \textbf{Cooper, K. W.}. (2017) Indiana University Undergraduate Research Conference. 
     
	
    \item Downstream Hippocampal Activity Prediction with Neural Networks\\ \textbf{Cooper, K. W.}, Osborn, Z.. (2016) Midwest Undergraduate Cognitive Science Conference. 
     
	


\end{etaremune}







%------------------------------------------------------------------------------
%	
%------------------------------------------------------------------------------





%------------------------------------------------------------------------------
%	TEACHING
%------------------------------------------------------------------------------

\section{Teaching}


 
\begin{longtable}{@{} l @{\extracolsep{\fill}} l @{\extracolsep{\fill}} l @{\extracolsep{\fill}} l @{}}

\textcolor{grey}{\textit{as Co-Instructor:}} & & \textcolor{grey}{\textit{enrollment:}} & \\


 Continual Learning & \textcolor{grey}{\textit{Neuromatch}} &  \textcolor{grey}{\textit{5000+}} & \textcolor{grey}{\textit{Su}} \hspace{0.05cm} 2021\\



 Autonomous Robotics & \textcolor{grey}{\textit{Indiana Univ.}} &  \textcolor{grey}{\textit{18}} & \textcolor{grey}{\textit{Sp}} \hspace{0.05cm} 2019\\



 Programming in Cognitive Sciences & \textcolor{grey}{\textit{Indiana Univ.}} &  \textcolor{grey}{\textit{27}} & \textcolor{grey}{\textit{Sp}} \hspace{0.05cm} 2018\\


\\
\textcolor{grey}{\textit{as Teaching Assistant:}} & & \textcolor{grey}{\textit{enrollment:}} & \\


 Mind, Memory, and the Brain & \textcolor{grey}{\textit{UC Irvine}} &  \textcolor{grey}{\textit{142}} & \textcolor{grey}{\textit{Sp}} \hspace{0.05cm} 2021\\



 Neurobiology and Behavior Laboratory & \textcolor{grey}{\textit{UC Irvine}} &  \textcolor{grey}{\textit{196}} & \textcolor{grey}{\textit{Wt}} \hspace{0.05cm} 2020\\



 Neurobiology and Behavior Laboratory & \textcolor{grey}{\textit{UC Irvine}} &  \textcolor{grey}{\textit{93}} & \textcolor{grey}{\textit{Fa}} \hspace{0.05cm} 2020\\



 Brain and Behavior & \textcolor{grey}{\textit{UC Irvine}} &  \textcolor{grey}{\textit{366}} & \textcolor{grey}{\textit{Fa}} \hspace{0.05cm} 2020\\



 Cognitive Psychology & \textcolor{grey}{\textit{Indiana Univ.}} &  \textcolor{grey}{\textit{80}} & \textcolor{grey}{\textit{Fa}} \hspace{0.05cm} 2018\\



 Introduction to Neuroscience & \textcolor{grey}{\textit{Indiana Univ.}} &  \textcolor{grey}{\textit{106}} & \textcolor{grey}{\textit{Fa}} \hspace{0.05cm} 2017\\


\\
\end{longtable}



% networks: # add active and inactive?
%   - societies:
%     - whenName: present
%     - names: 





%------------------------------------------------------------------------------
%	
%------------------------------------------------------------------------------





%------------------------------------------------------------------------------
%	MENTEES
%------------------------------------------------------------------------------

\section{Mentored Students}
\begin{longtable}{@{} l  l @{}}
 
Tien Lam &  \textcolor{gray}{\textit{ now preparing for medical school}}  \\
 
Brandon McIntosh &  \textcolor{gray}{\textit{ now preparing for medical school}}  \\
 
Chelsea Pan &  \textcolor{gray}{\textit{ now Zendesk}}  \\
 
Troy Good &  \textcolor{gray}{\textit{ now Amazon}}  \\

\end{longtable}






%------------------------------------------------------------------------------
%	
%------------------------------------------------------------------------------





%------------------------------------------------------------------------------
%	NETWORKS
%------------------------------------------------------------------------------
% Have to do some funky stuff here to get the columns right

\section{Networks}

\begin{longtable}{@{} l @{\extracolsep{\fill}} l}


\textcolor{grey}{\textit{Present:}}\\

	Cognitive Science Society & Society for Neuroscience\\

	Continual AI (co-founder) & Indiana Academy of Science\\

	Global Consortium for Chemosensory Research & Psi Chi\\

	Sigma Xi & Sigma Alpha Pi\\

	Carboncopies Foundation & AI for People\\

	Internet Society & \\


\\

\textcolor{grey}{\textit{Past:}}\\

	IU Student Org. for Cog Sci (President) & ADAPT Consulting (VP)\\


\\
\end{longtable}







%------------------------------------------------------------------------------
%	
%------------------------------------------------------------------------------





%------------------------------------------------------------------------------
%	SCICOMM
%------------------------------------------------------------------------------

\section{SciComm + Outreach}

\begin{longtable}{@{} l @{\extracolsep{\fill}}  l @{}}
	 
	AskANeuroscientist & \textcolor{grey}{ \textit{Founder; Live Q/A via in class video-chat (>400 students)}} \\
	 
	Hoosier STARS & \textcolor{grey}{ \textit{Co-founder; K-12 neuro demos reaching >300 students}} \\
	 
	Quora Writer & \textcolor{grey}{ \textit{Answers to neuroscience and AI questions (800k+ views)}} \\
	 
	CNLM Ambassadors & \textcolor{grey}{ \textit{Co-chair; SoCal Learning and memory outreach}} \\
	 
	The Boys and Girls Club & \textcolor{grey}{ \textit{Taught primary school aged students about the brain}} \\
	 
	IU Science Fest & \textcolor{grey}{ \textit{Led a booth with hands on sheep brain interaction}} \\
	 
	Celebrate Science Indiana & \textcolor{grey}{ \textit{Led an EEG and brain booth > 500 people}} \\
	 
	Observatory Guide & \textcolor{grey}{ \textit{Volunteer astronomical guide at the Kirkwood Observatory}} \\
	
\end{longtable}






%------------------------------------------------------------------------------
%	
%------------------------------------------------------------------------------





%------------------------------------------------------------------------------
%	UNIVERSITY SERVICE
%------------------------------------------------------------------------------

\section{University Service}
\begin{longtable}{@{} l  l @{\extracolsep{\fill}} l @{}}
 
UC Advocacy Network Campus Leader & \textcolor{gray}{\textit{University of California, Irvine}} & \textit{2021 -} \\
 
End Racism Initiative & \textcolor{gray}{\textit{University of California, Irvine}} & \textit{2020 -} \\
 
Education Policy Committee & \textcolor{gray}{\textit{Indiana University}} & \textit{2016 - 2017} \\
 
Faculty Council & \textcolor{gray}{\textit{Indiana University}} & \textit{2016 - 2017} \\
 
Office of First Year Experience & \textcolor{gray}{\textit{Indiana University}} & \textit{2015 - 2016} \\

\end{longtable}







%------------------------------------------------------------------------------
%	
%------------------------------------------------------------------------------





%------------------------------------------------------------------------------
%	REFEREE SERVICE
%------------------------------------------------------------------------------

\section{Referee Service}
\begin{longtable}{@{} l @{\extracolsep{\fill}}  l @{}}
 
Physiological Reviews & \\
 
CLVision @ CVPR & \\

\end{longtable}





%------------------------------------------------------------------------------
%	
%------------------------------------------------------------------------------





%------------------------------------------------------------------------------
%	TRAININGS -n- WORKSHOPS
%------------------------------------------------------------------------------

\section{Trainings + Workshops}

\begin{longtable}{@{} l l @{\extracolsep{\fill}}  l @{}} 
	 
	Mental Health First Aid & \textcolor{gray}{Nat. Council for Mental Wellbeing}  & \textit{2021} \\
	 
	FFASt Workshop on Scientific Leadership & \textcolor{gray}{UC Irvine}  & \textit{2021} \\
	 
	Certified Peer Reviewer & \textcolor{gray}{Elsevier}  & \textit{2020} \\
	 
	Computational Psychiatry Course & \textcolor{gray}{University of Zurich}  & \textit{2020} \\
	 
	The Meaning and History of the Constitution & \textcolor{gray}{Hillsdale College}  & \textit{2020} \\
	 
	Estes Cognitive Electrophysiology Workshop & \textcolor{gray}{University of Pennsylvania}  & \textit{2020} \\
	 
	NIH Grant Writing Workshop & \textcolor{gray}{UC Irvine}  & \textit{2020} \\
	 
	HHMI Productivity Workshop & \textcolor{gray}{UC Irvine}  & \textit{2020} \\
	 
	Nonlinear Dynamics: Math. and Comp. & \textcolor{gray}{Santa Fe Institute}  & \textit{2019} \\
	 
	Complexity Science & \textcolor{gray}{Santa Fe Institute}  & \textit{2018} \\
	 
	Science Communication Workshop & \textcolor{gray}{Indiana University}  & \textit{2017} \\
	 
	High Performance Supercomputing Workshop & \textcolor{gray}{Indiana University}  & \textit{2017} \\
	 
	Aseptic Surgery: Proper Practice Training & \textcolor{gray}{Indiana University}  & \textit{2016} \\
	 
	Animal Handling and Animal Care Training & \textcolor{gray}{Indiana University}  & \textit{2016} \\
	 
	IUNI Network Science Workshop & \textcolor{gray}{Indiana University}  & \textit{2016} \\
	 
	First Aid and CPR Certified & \textcolor{gray}{American Red Cross}  & \textit{2014} \\
	 
	Pediatric Neurosurgery Shadowing & \textcolor{gray}{Riley Hospital}  & \textit{2014} \\
	
\end{longtable}








%------------------------------------------------------------------------------
%	
%------------------------------------------------------------------------------





%------------------------------------------------------------------------------
%   DATASETS
%------------------------------------------------------------------------------

\section{Open\\Datasets}

 
\begin{etaremune}[itemindent=-1.5\bibhang, topsep=0pt,
                   itemsep=\bibsep,partopsep=0pt,parsep=0pt,leftmargin={\bibhang+\widthof{[999]}}] 
    
    \item \href{https://doi.org/10.7280/D14X30}{Hippocampal ensembles represent sequential relationships among an extended sequence of nonspatial events} (2021) Dryad
    
    \item \href{https://osf.io/a3vkw/}{GCCR COVID-19 Questionnaire} (2020) OSF
    
    \item \href{https://crcns.org/data-sets/hc/hc-27/about-hc-27}{Extracellular recordings from across the dorsoventral axis of the medial entorhinal cortex of the rat. hc-27} (2020) CRCNS
    

\end{etaremune}








%------------------------------------------------------------------------------
%	
%------------------------------------------------------------------------------





%------------------------------------------------------------------------------
%	NON PEER PUBS
%------------------------------------------------------------------------------
% Add the rule here so that we can use varrying subsections 

% \needspace{\headerpush}
% \myRule{\columnwidth}{1pt}\\
\section{Essays} 

 
\begin{etaremune}[itemindent=-1.5\bibhang, topsep=0pt,
				   itemsep=\bibsep,partopsep=0pt,parsep=0pt,leftmargin={\bibhang+\widthof{[999]}}] 
    
    \item The Art of Email \\
     Keiland Cooper. (Febuary 18, 2020) GPS-STEM
     
	
    \item The Psychology of Risky Business \\
     Keiland Cooper. (July 23, 2018) Medium
     
	
    \item Save Money, Close Deals, Clip Coupons: the Science of Decision Making \\
     Keiland Cooper. (July 11, 2018) Medium
     
	
    \item The <Art> of Biting your Tongue \\
     Keiland Cooper. (October 19, 2017) LinkedIn Publishing
     
	
    \item What Is Undergraduate Research And Why Is It Important? \\
     Keiland Cooper. (September 7, 2017) We Are IU
     
	
    \item The Silent Battle for the Web May Change Everything as We Know It. \\
     Keiland Cooper. (December 5, 2016) Medium
     
	
    \item The What’s and Why’s of Schools App \\
     Keiland Cooper. (August 5, 2015) We Are IU
     
	

\end{etaremune}








%------------------------------------------------------------------------------
%	
%------------------------------------------------------------------------------





%------------------------------------------------------------------------------
%	PRESS
%------------------------------------------------------------------------------

\section{Press}

 
\begin{etaremune}[itemindent=-1.5\bibhang, topsep=0pt,
				   itemsep=\bibsep,partopsep=0pt,parsep=0pt,leftmargin={\bibhang+\widthof{[999]}}] 
    
    
    \item  (March 7, 2022) \textit{Study reveals how the brain organizes memories}. Al Jazeera
     
	
    \item Mary McGorray (January 14, 2022) \textit{Predicting Alzheimer’s risk: Why cognitive testing alone may not work.}. Medical News Today
     
	
    \item David Oliver (December 22, 2021) \textit{Has COVID destroyed our attention spans?}. USA Today
     
	
    \item Jeanna D. Smiley (November 21, 2021) \textit{Why are human neurons different from those of other mammals?}. Medical News Today
     
	
    \item Kyle Wiggers (April 9, 2021) \textit{AI Weekly: Continual learning offers a path toward more humanlike AI}. VentureBeat
     
	
    \item  (April 8, 2021) \textit{ContinualAI Releases Avalanche: An End-to-End Library for Continual Learning}. Synced Review
     
	
    \item Grace Hauck (January 31,2021) \textit{Millions of COVID-19 survivors have lost senses of smell and taste. Researchers don't know if they'll come back}. USA Today
     
	
    \item Brooke Jarvis (January 28, 2021) \textit{What Can Covid-19 Teach Us About the Mysteries of Smell?}. The New York Times Magazine
     
	
    \item Misha Gajewski (December 9, 2020) \textit{Is Losing Your Sense Of Smell And Taste The First Sign Of Covid-19? More Research Says Yes}. Forbs
     
	
    \item Vincent Racaniello (October 18, 2020) \textit{TWiV 673: Wake up and smell the pandemic}. This Week In Virology
     
	
    \item Sara Harrison (August 5, 2020) \textit{Many COVID-19 patients lost their sense of smell. Will they get it back?}. National Geographic
     
	
    \item Bob Curley (July 7, 2020) \textit{Lifestyle Changes You Can Make to Help Lower the 19 Risk Factors for Alzheimer’s}. Healthline
     
	
    \item Salynn Boyles (July 6, 2020) \textit{Majority of Patients with Mild Covid-19 Experience Altered Smell/Taste}. Physicians Weekly
     
	
    \item Katie Boateng (June 15, 2020) \textit{Episode 64 - An Interview with Some of the Authors}. The Smell Podcast
     
	
    \item Leslie Kay (June 13, 2020) \textit{Why COVID-19 Makes People Lose Their Sense of Smell}. Scientific American
     
	
    \item John E Hayes, Valentina Parma (June 4, 2020) \textit{COVID-19, smell and taste – how is COVID-19 different from other respiratory diseases? }. The Conversation
     
	
    \item Anthony Cusumano (February 2, 2020) \textit{What a difference a decade makes.}. Katalys Tech
     
	
    \item Kevin Casey (September 30, 2019) \textit{5 AI fears and how to address them.}. The Enterprisers Project
     
	
    \item Kevin Casey (September 17, 2019) \textit{How to explain natural language processing (NLP) in plain English}. The Enterprisers Project
     
	
    \item David Roe (August 27, 2019) \textit{Is Augmented Artificial Intelligence Already Disrupting Artificial Intelligence?}. CMS Wire
     
	
    \item Kristine Fellizar (August 7, 2019) \textit{Why Is My Arm Asleep? 6 Reasons Your Limbs Go Numb When You're Sleeping}. Bustle
     
	
    \item Lauren Wellbank (August 1, 2019) \textit{Neuralink Update: How far off is Elon Musk’s high tech vision for our brains?}. Parentology
     
	
    \item Tina Arnoldi (July 19, 2019) \textit{Ready for Amazon to Read Human Emotions?}. Theravive
     
	
    \item Ann Lewandowski (September 28th, 2018) \textit{IU undergraduates practice science outreach at Indiana high schools}. IDS
     
	
    \item Alexandra Moussa-Tooks (August 14, 2018) \textit{The art of dissemination part 3: Care to share?}. ScIU
     
	
    \item Liz Rosdeitcher (2017) \textit{Community Partnerships.}. Psyugrad
     
	


\end{etaremune}



%------------------------------------------------------------------------------
%	REF
%------------------------------------------------------------------------------

%\section{References Available to Contact}
%
%Available upon request. 
%






%------------------------------------------------------------------------------
%	
%------------------------------------------------------------------------------





%------------------------------------------------------------------------------
%	ERDOS
%------------------------------------------------------------------------------


\section{Erdös N=3}
% https://www.csauthors.net/distance/paul-erdos/keiland-cooper

\textit{\textcolor{grey}{as of 2022:}}\\
Paul Erdös $\rightarrow$ Richard M. Wilson $\rightarrow$ Pierre F. Baldi $\rightarrow$ me\\


\textit{\textcolor{grey}{as of 2021:}}\\
Paul Erdös $\rightarrow$ Noga Alon $\rightarrow$ Nicolò Cesa-Bianchi $\rightarrow$ Fabio Cuzzolin $\rightarrow$ me\\


\textit{\textcolor{grey}{as of 2019:}}\\
Paul Erdös $\rightarrow$ Ronald Graham $\rightarrow$ Feng Zhou $\rightarrow$ Michael Kahana $\rightarrow$ Ehren Newman $\rightarrow$ me\\








%------------------------------------------------------------------------------
%	
%------------------------------------------------------------------------------








% \newpage


% \hspace*{-\marginparsep minus \marginparwidth}%
%  \begin{minipage}[t]{\textwidth+\marginparwidth+\marginparsep}%

% \textbf{{\huge Keiland W. Cooper }} {\large data sheet} \hfill \\ 
% [-0.15\baselineskip]%
% \rule{\columnwidth}{1pt}%
% \end{minipage}

% \vspace{2\baselineskip}
% \begin{minipage}[t]{\textwidth+\marginparwidth+\marginparsep}%
% {\huge Publication Statistics: }\\
% 	\factbubble{\huge{\textcolor{white}{\textbf{335}}}\\\small{\textcolor{white}{citations}} }{1}{white}{gray}{black}
% 	\factbubble{\huge{\textcolor{white}{\textbf{5}}}\\\small{\textcolor{white}{h-index}} }{1}{white}{gray}{black}
% 	\factbubble{\huge{\textcolor{white}{\textbf{5}}}\\\small{\textcolor{white}{i10index}} }{1}{white}{gray}{black}\\

% % \parbox[c][3cm][c]{0.32\textwidth}{
% % 	\begin{center}
% % 	\factbubble{\huge{\textcolor{white}{\textbf{5}}}\\\small{\textcolor{white}{h-index}} }{1}{white}{gray}{black}\\
% % 	% \textcolor{black}{as latest degree from}\\
% % 	% \textcolor{black}{\textbf{University of Bremen}}
% % 	\end{center}
% % }
% \end{minipage}



% \vspace{2\baselineskip}
% \begin{minipage}[t]{.45\textwidth}%
% \raggedright
% {\large \# publications}\\

% 	\begin{barchart}{5.5}
% 		\baritem{2018}{10}{1}
% 		\baritem{2019}{0}{0}
% 		\baritem{2020}{60}{6}
% 		\baritem{2021}{10}{1}
% 		\baritem{2022}{0}{0}
% 	\end{barchart}
% \end{minipage}%
% \vspace{2\baselineskip}
% \begin{minipage}[t]{.45\textwidth}%
% \raggedright
% {\large \# Citations}\\

% 	\begin{barchart}{5.5}
% 		\baritem{2018}{60}{3}
% 		\baritem{2019}{100}{10}
% 		\baritem{2020}{70}{100}
% 		\baritem{2021}{70}{4}
% 		\baritem{2022}{40}{3}
% 	\end{barchart}
% \end{minipage}



% \vspace{2\baselineskip}
% \begin{minipage}[t]{\textwidth+\marginparwidth+\marginparsep}%
% {\huge Skills}\\
% 	\bubbles{5/Eclipse, 6/git, 4/Office, 3/Inkscape, 3/Blender, 6/git, 4/Office, 3/Inkscape}
% \end{minipage}




\end{document}