\cvsection{Publications}
\begin{cvpubentries}

% to do: update class
% add links

%---------------------------------------------------------
\iftrue
  \cvpubentry
    {In preperation} % Role
    { } % Title
    { } % Location
    { } % Date(s)
    {
      \begin{cvpubitems} % Description(s)
        \item {Hernandez, J. Cooper, K.W. (2018) Is Theta a Traveling Wave in the Entorhinal Cortex?}
      \end{cvpubitems}
    }
\fi

%---------------------------------------------------------
\iffalse
  \cvpubentry
    {In press} % Role
    {} % Title
    {} % Location
    {} % Date(s)
    {
      \begin{cvpubitems} % Description(s)
        \item {pub}
      \end{cvpubitems}
    }
\fi

%---------------------------------------------------------
  \cvpubentry
    {Published} % Role
    {} % Title
    {} % Location
    {} % Date(s)
    {
      \begin{cvpubitems} % Description(s)
        \item {Cooper K.W. (2018) Can the Machine Understand: An Evidence Based Approach to the Chinese Room. IUJUR}
      \end{cvpubitems}
    }
%---------------------------------------------------------
\iffalse % for space, ratchet, i know
\fi

\cvpubentry
    {Selected Abstracts/Presentations} % Role
    {} % Title
    {} % Location
    {} % Date(s)
    {
      \begin{cvpubitems} % Description(s)
        \item {Cooper K.W, Dachapally P.R, Jones M.N (2018) Consequences of Catastrophic Forgetting on Semantic Representations Learned by Deep Neural Embedding Models Midwest CogSci}
	\item{Cooper K.W., Hernandez J, Newman E.L. (2018) Is theta in the Medial Entorhinal Cortex a Traveling Wave? Society for Neuroscience, Greater Indiana Chapter.}
	\item{Cooper K. W. (2018) 3D Brain Model Extraction and Virtual Applications. (Panelist) Media School Graduate Association Conference.}
	\item{Cooper K. W. (2017) Bridging the Gap: Natural Computation and Neural Systems. Indiana University Undergraduate Research Conference.}
	\item{Cooper K. W., Osborn Z. (2016) Downstream Hippocampal Activity Prediction with Neural Networks. Midwest Undergraduate Cognitive Science Conference.}
      \end{cvpubitems}
    }

\end{cvpubentries}
