\cvsection{Publications}
\begin{cvpubentries}

% to do: update class
% add links

%---------------------------------------------------------
\iffalse
  \cvpubentry
    {\textit{In preparation}} % Role
    { } % Title
    { } % Location
    { } % Date(s)
    {
      \begin{cvpubitems} % Description(s)
        \item { Paper goes here }
      \end{cvpubitems}
    }
\fi

%---------------------------------------------------------
\iftrue
  \cvpubentry
    {\textit{In review}} % Role
    { } % Title
    { } % Location
    { } % Date(s)
    {
      \begin{cvpubitems} % Description(s)
        \item {Perez, J. J. H., Cooper, K. W., \& Newman, E. L. (2019). Medial entorhinal cortex activates in a traveling wave. BioRxiv, 632109. }
      \end{cvpubitems}
    }
\fi

%---------------------------------------------------------
\iffalse
  \cvpubentry
    {\textit{In press}} % Role
    {} % Title
    {} % Location
    {} % Date(s)
    {
      \begin{cvpubitems} % Description(s)
        \item {pub}
      \end{cvpubitems}
    }
\fi

%---------------------------------------------------------
  \cvpubentry
    {\textit{Published}} % Role
    {} % Title
    {} % Location
    {} % Date(s)
    {
      \begin{cvpubitems} % Description(s)
        \item {Cooper, K. W. (2018). Can the Machine Understand: An Evidence Based Approach to the Chinese Room. IU Journal of Undergraduate Research, 4(1), 82-85.}
      \end{cvpubitems}
    }
%---------------------------------------------------------
\iffalse % for space, ratchet, i know
\fi

\cvpubentry
    {\textit{Abstracts/Presentations}} % Role
    {} % Title
    {} % Location
    {} % Date(s)
    {
      \begin{cvpubitems} % Description(s)
	\item{Hernández J, Cooper K.W., Newman E.L. (2018) Is theta a traveling wave in the medial entorhinal cortex?. Program No. 330.10. Society for Neuroscience, 2018}
        \item {Cooper K.W, Dachapally P.R, Jones M.N (2018) Consequences of Catastrophic Forgetting on Semantic Representations Learned by Deep Neural Embedding Models Midwest CogSci}
	\item{Cooper K.W., Hernández J, Newman E.L. (2018) Is theta in the Medial Entorhinal Cortex a Traveling Wave? Society for Neuroscience, Greater Indiana Chapter.}
	\item{Cooper K. W. (2018) 3D Brain Model Extraction and Virtual Applications. (Panelist) Media School Graduate Association Conference.}
	\item{Cooper K.W. (2018) FlapAI: Genetically Evolved Neural Networks. Midwest Undergraduate Cognitive Science Conference}
	\item{Cooper K. W. (2017) Bridging the Gap: Natural Computation and Neural Systems. Indiana University Undergraduate Research Conference.}
	\item{Cooper K. W., Osborn Z. (2016) Downstream Hippocampal Activity Prediction with Neural Networks. Midwest Undergraduate Cognitive Science Conference.}
      \end{cvpubitems}
    }

\end{cvpubentries}
