\cvsection{Research Projects}
\begin{cventries}

% This likely needs to be updated with the changes to the design file, 
% ie. renaming cvitems to cvpritems etc.
%---------------------------------------------------------
  
\cvrpentry
    {With Dr. Ehren Newman: Neural Correlates of Learning and Memory} % Job title
    {} % Organization
    {} % Location
    {2015 - Present } % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Hippocampal Mode Switching computational model}
	\item{Traveling Theta Wave in the Entorhinal Cortex}
	\item{CA1 Assembly Flouresence Imaging}
	\item{Optic Flow and Theta Modulation}
      \end{cvitems}
    }

\cvrpentry
    {With Dr. Mike Jones: Computational Cognitive Science, Artificial Intelligence} % Job title
    {} % Organization
    {} % Location
    {2018 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Overcoming Catastrophic forgetting in connectionist embedding models.}
      \end{cvitems}
    }

\cvrpentry
    {With Dr. Fredric Schmitt: Philosophy of Mind} % Job title
    {} % Organization
    {} % Location
    {2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Can the Machine Think? An evidence based approach .}
      \end{cvitems}
    }

\cvrpentry
    {With Dr. Amit Hagar: History and Philosophy of Science; Quantum Computing} % Job title
    {} % Organization
    {} % Location
    {2017 - 2018 } % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {The Natural Computation of the Brain}
      \end{cvitems}
    }

\cvrpentry
    {With Ressl Lab: Biochemical Structure of proteins in Synaptic Connectivity} % Job title
    {} % Organization
    {} % Location
    {2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Investigating the Structure of Membrane Protein YejM}
      \end{cvitems}
    }

\cvrpentry
    {Independant} % Job title
    {} % Organization
    {} % Location
    {2016 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Predicting Hippocampal CA1 activity with machine learning}
	\item {Evolving neural networks to play games}
      \end{cvitems}
    }

\cvrpentry
    {As part of program} % Job title
    {} % Organization
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {fMRI Data analysis - with Dr. Tom James, Dr. Josh Brown}
	\item {Autonomous Robotics - with Dr. Randall Beer}
	\item{Human EEG - with Dr. Ben Ramsden }
      \end{cvitems}
    }




\end{cventries}